---
title: "Nasdaq Returns 2012-16"
author: "MD"
date: "20. März 2016"
output: ioslides_presentation
runtime: shiny
---

## Course Project

```{r, echo=FALSE, message=FALSE}
require(quantmod)
library(dygraphs)
```
We would like to interactively find out about the stock
price distribution of the NASDAQ index.
Hence **we** will conduct the following analysis:

- Get the data from finance.yahoo.com
- Clean & transform the price to return data (i.e. our dataset of interest)
- create a server.R shinyApp backend component to return data for specific time ranges
- cretae a UI.r shinyApp frontend component to let the user select time ranges of interest

to finally create an interactive histogram chart of the nasdaq index returns.

## Get the data

On finance.yahoo.com we find out the Nasdaq Composite Index (ticker symbol **IXIC**) historical prices can be downloaded under the url (**ndq_data_url**) we use to csv.read our analysis data from:

```{r}
ndq_data_url = "http://real-chart.finance.yahoo.com/table.csv?s=%5EIXIC&d=2&e=20&f=2016&g=d&a=1&b=5&c=1971&ignore=.csv"
ndq_data = read.csv(ndq_data_url)
ndq_data = ndq_data[ ,c('Date', 'Close')]
head(ndq_data)
ndq_xts = xts(ndq_data[,-1],order.by=as.POSIXct(ndq_data$Date))
ret<-diff(log(ndq_data$Close))
head(ndq_data)
```

## TimeSeries of Prices

```{r, echo=FALSE}
dygraph(ndq_xts)
```

## Distribution of Log Returns

```{r, echo=FALSE}
inputPanel(
  selectInput("hist_bins", label = "Histogram #Bins",
              choices = c(10, 20, 30, 40, 50), selected = 30)
  
)
renderPlot({
  hist(ret, probability = TRUE, breaks = as.numeric(input$hist_bins),
       xlab = "Log Return", main = "Nasdaq Log Return Distribution")
})
```


